### 2013-05-24 drafts/general_writeup/writeup.tex
Modifications to GP section of general writeup.
Started section on density estimation with program planning.

@@

>>>>

\subsection{Software}
from page 148 of \cite{poli08:fieldguide}:
\begin{itemize}
\item Lil-GP (Punch and Zongker, 1998)
\item ECJ (Luke, Panait, Balan, Paus, Skolicki, Popvici, Harrison, Bassett,
Hubley, and Chircop, 2000-2007)
\item Open Beagle (Gahge and Parizeau, 2002)
\item GPC++ (Fraser and Weinbrenner)
\item commercial: Discipulus (RML Technologies)
\item review: Foster, 2001 
\end{itemize}

@@

\section{Density estimation with program planning} 
Density estimation -- an unsupervised learning task whose importance is
increasing in modern machine learning -- is the process of learning the
probability density function associated with some set of data. The utility of
doing this comes from the fact that a low dimensional representation of the
learned density function is useful in other tasks.

Suppose, for example, that we wanted to learn the distribution over real-world
images from a dataset of images that we download from the web. The space of
possible images is extremely large, but space of images that are probable in
the real world is vanishingly small within the space of all possible images. To
learn the distribution of images means that a new real world image will be
assigned a relatively high likelihood under our learned distribution and noise,
for example, would be assigned a low likelihood.
